CommonMind Consortium: DLPFC

### 2020-09-18 combined_analysis/diff.networks.Rmd
Update diff networks

## Module enrichment
```{r top.enrich.Dx}

enrich.test = function(df_module, gs){

	res = lapply( unique(df_module$Module), function(mod){

			genes = df_module[df$]

		})

}

```

@@

@@

>>>>

```{r exit, cache=FALSE, eval=FALSE}
knitr::knit_exit()
```

## Module enrichment
```{r top.enrich.Sex}
df_module = data.frame(	ENSEMBL = rownames(C.diff.discovery) %>% trim_ensembl_ids, 
						Module = dynamicColors.Sex)

df_module_enrich.Sex = enrich.test( df_module, go.gs, df_cohort2$Module[i])
```

plot_enrich(df_module_enrich.Sex[1:10,], module) + ggtitle()

@@

## Module enrichment
```{r top.enrich.Sex}
df_module = data.frame(	ENSEMBL = rownames(C.diff.discovery) %>% trim_ensembl_ids, 
						Module = dynamicColors.Dx)

df_module_enrich.Dx = enrich.test( df_module, go.gs, df_cohort2$Module[i])
```

@@

## Module enrichment
```{r top.enrich.Sex}
df_module = data.frame(	ENSEMBL = rownames(C.diff.discovery) %>% trim_ensembl_ids, 
						Module = dynamicColors.Dx_Sex)

df_module_enrich.Dx_Sex = enrich.test( df_module, go.gs, df_cohort2$Module[i])
```
